Experience Report: Haskell in Computational Biology

### 2012-03-11 mrfy_experience_report.tex
consistent font sizes
remind what an Experience Report is

\begin{abstract}
Haskell combines the flexibility and rapid prototyping of a scripting
language with performance comparable to~C++.
The Haskell language and libraries provide powerful abstractions, 
but we couldn't always get them to work!
Despite some speed bumps around profiling, debugging, and the
uncertain status of any given package, we~found Haskell's ecosystem
provided fine support for developing new algorithms in computational
biology.
\end{abstract}

@@

Our implementation computes not only the minimum
negated log probability, called a \texttt{Score},
but also the path of states which leads to that most likely outcome. 
Elsewhere, MRFy pairs not only paths but also other types of values
with scores, so we have defined a small abstraction:
\verbatiminput{vscore}
We~made \texttt{Scored} an instance of~\texttt{Ord} and of
\texttt{Functor}.

>>>>

\begin{abstract}
The Experience Report series is
a body of published, refereed, citable \emph{evidence} that functional
programming really works---or descriptions of obstacles that prevent
it from working.   
In~this Experience Report, we show that for computational biologists,
Haskell combines the flexibility and rapid prototyping of a scripting
language with performance comparable to~C++.
The Haskell language and libraries provide powerful abstractions, 
but we couldn't always get them to work!
Despite some speed bumps around profiling, debugging, and the
uncertain status of any given package, we~found Haskell's ecosystem
provided fine support for developing new algorithms in computational
biology.
\end{abstract}

@@

Our implementation computes not only the minimum
negated log probability, called a \texttt{Score},
but also the path of states which leads to that most likely outcome. 
Elsewhere, MRFy pairs not only paths but also other types of values
with scores, so we have defined a small abstraction:
\smallverbatiminput{vscore}
We~made \texttt{Scored} an instance of~\texttt{Ord} and of
\texttt{Functor}.
